Stabilization-Free Virtual Element Methods

### 2023-03-11 reports/response.tex

\medskip

\item \textsf{Lines 17-18; when you discuss the results in references \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, I am not quite sure that the polynomial degree of the projection depends only on the number of vertices. In fact, in an updated version of the preprint \cite{BerroneBorioMarcon2021}, it is possible to see that also the shape of the polygon plays a role in the choice of such a polynomial degree.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. In \cite{BerroneBorioMarcon2021}, the polynomial degree $l$ should satisfy
$$
(l+1)(l+2) - \dim\mathcal{P}_l^{\textrm{ker}}(E)\geq N_E^V-1.
$$
And the dimension of $\mathcal{P}_l^{\textrm{ker}}(E)$ generally depends on the geometry of the polygon. While the authors prove that
$$
\dim\mathcal{P}_l^{\textrm{ker}}(E)\leq l(l+1)
$$
in \cite[Theorem 2]{BerroneBorioMarcon2021}. This means that a sufficient condition for $l$ is 
$$
l\geq \frac{1}{2}(N_E^V-3).
$$

@@

To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we only require
$(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ to be a polynomial for each $(d-1)$-dimensional face $F$ of $K$. But $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ can be a piecewise polynomial for interior face $F$ of the simplicial tessellation of $K$.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Now we use $\mathbb P_{k-2}^{\perp}(K)$ to denote the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.

\medskip

\item \textsf{You may wish to shorten up or even remove the proof of Lemma 4.1, which is standard in the virtual element literature.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
One reviewer has questions on the proof of Lemma 4.1, and the proof of Lemma 4.1 is also helpful for the proof of Lemma 4.3. Thus we modify the proof and keep it.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have revised DoFs (5.1), (5.2), and (5.3) as
\begin{align*}
v(\delta), & \quad \delta\in\mathcal V(K), \\
\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K),
\end{align*}
where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.

\medskip

\item \textsf{You may wish to reduce or even drop the proof of Theorem 5.3, which appears to be a standard Strang-type result for the VEM.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have removed the proof of Theorem 5.3.
We combine Section 5.2 and Section 5.3 in the revised manuscript.

@@

For the second question, it can be explained as follows:
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$

\medskip

\item \textsf{In the proof of Lemma 4.1, the authors claim that
$$
h_K^{\frac{1}{2}}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
$$
This is a sort of discrete trace inequality and the authors justify it by citing (A.3)-(A.4) in [15]. However, it is not apparent to me how this follows from (A.3)-(A.4). Moreover, the authors conclude that “with the multiplicative trace inequality”
$$
h_K^{\frac{1}{2}}\|v\|_{0,\partial K}\lesssim h_K^{-1}\|v\|_{0,K}.
$$
Again, this is a discrete trace inequality, and it is not specified why it is valid on the virtual space $V_k(K)$. The same goes for the arguments used in the proof of Lemma 4.3.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
% One reviewer suggests removing the proof of Lemma 4.1, as it is standard in the virtual element literature. We agree with his suggestion, so we remove the proof of Lemma 4.1 in the revised manuscript. But we explain this comment in detail, and provide a complete proof of Lemma 4.1 here. 
\begin{itemize}
    \item 
For virtual function $v\in V_k(K)$, apply (A.3) in \cite{ChenHuang2020ncvem} to get
\[
h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
\]
By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
\[
h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
\]
Combining the last two inequalities yields
\[
h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
\]
\item The multiplicative trace inequality is
\[
\|v\|_{0,\partial K}\lesssim h_K^{-1/2}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \quad\forall~v\in H^1(K).
\]
Since $v\in V_k(K)\subset H^1(K)$, inserting the last multiplicative trace inequality into the inequality
\[
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
\]
we get
\begin{align*}
|v|_{1,K}&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \\
&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,K}^{1/2}|v|_{1,K}^{1/2}.
\end{align*}
Then apply the Young's inequality to acquire the inverse inequality
\begin{equation*}%\label{eq:veminverse}
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}\quad\forall~v\in V_k(K).  
\end{equation*}
\end{itemize}

% \vskip0.2cm
% \noindent\textcolor{cyan}{The complete proof of the inverse inequality \eqref{eq:veminverse} (i.e. Lemma 4.1) is given as follows.}
% \vskip0.2cm

% By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
% \[
% h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
% \]
% Then apply (A.3) in \cite{ChenHuang2020ncvem} to get
% \[
% h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
% \]
% Employing the integration by parts and the Cauchy-Schwarz inequality, we have
% \[
% |v|_{1,K}^2=-(\Delta v,v)_K+(\partial_nv,v)_{\partial K}\leq\|\Delta v\|_{0,K}\|v\|_{0,K}+\|\partial_nv\|_{0,\partial K}\|v\|_{0,\partial K}.
% \]
% Combining the last two inequalities gives
% \[
% |v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
% \]
% which together with the multiplicative trace inequality and the Young's inequality yields the inverse inequality \eqref{eq:veminverse}.

### 2023-03-11 stabfreevem_sinum.tex

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x},
\end{equation}
\XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
% $$
% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
% $$
% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.
}

@@

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:cfmvem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation} 
where the discrete bilinear form 
\[
a_h(u_h, v_h):=(Q_{h,k}^{\div}\nabla u_h, Q_{h,k}^{\div}\nabla v_h)+\alpha(Q_hu_h, Q_hv_h).
\]

It is obvious that 
\begin{equation}\label{eq:cfmahbounedness}
a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
\end{equation}   
And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
the coercivity
\begin{equation}\label{eq:cfmahcoercivity}
|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
\end{equation}  
Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.

\begin{remark}\rm
By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the virtual element method \eqref{eq:cfmvem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
\begin{equation*}
\begin{aligned}
(\boldsymbol{\phi}_h, \boldsymbol{\psi}_h) - (\boldsymbol{\psi}_h, \nabla u_h)&=0 \quad\quad\quad\quad\;\;\forall~\boldsymbol{\psi}_h\in\mathbb{V}_{h,k}^{\rm div},\\
(\boldsymbol{\phi}_h, \nabla v_h)+\alpha(Q_hu_h, Q_hv_h)&=(f, Q_hv_h)\quad\forall~v_h\in V_h.
\end{aligned} 
\end{equation*} 
\end{remark}

@@

\subsection{Error analysis}
Applying the standard error analysis for VEMs, we have the following error estimate for the VEM \eqref{eq:cfmvem}.
\begin{theorem}\label{thm:cfmerrorestimateH1}
Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:cfmvem}. Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
\begin{equation}\label{eq:cfmerrorestimateH1}
|u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
\end{equation}
\end{theorem}
% \begin{proof}
% Take any $v_h\in V_h$. 
% Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
% \[
% \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
% \]
% \[
% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
% \]
% Combining the last two inequalities gives
% \[
% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
% \]
% By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
% \begin{align*}
% |v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
% % &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
% \end{align*}
% Hence we get from the triangle inequality and the last two inequalities that
% \begin{align*}  
% |u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
% &\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
% \end{align*}
% By the arbitrariness of $v_h\in V_h$, we derive
% \[
% |u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
% \]
% At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
% \end{proof}

@@

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Figure \ref{fig:rate1}. We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Figure \ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
of nonconforming virtual element method \eqref{eq:vem} on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}

>>>>

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x},
\end{equation}
\XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
}
% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
% $$
% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
% $$
% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.

@@

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:cfmvem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation} 
where the discrete bilinear form 
\[
a_h(u_h, v_h):=(Q_{h,k}^{\div}\nabla u_h, Q_{h,k}^{\div}\nabla v_h)+\alpha(Q_hu_h, Q_hv_h).
\]
The stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.

% It is obvious that 
% \begin{equation}\label{eq:cfmahbounedness}
% a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
% \end{equation}   
% And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
% the coercivity
% \begin{equation}\label{eq:cfmahcoercivity}
% |v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
% \end{equation}  
% Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.

% \begin{remark}\rm
By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the virtual element method \eqref{eq:cfmvem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
\begin{equation*}
\begin{aligned}
(\boldsymbol{\phi}_h, \boldsymbol{\psi}_h) - (\boldsymbol{\psi}_h, \nabla u_h)&=0 \quad\quad\quad\quad\;\;\forall~\boldsymbol{\psi}_h\in\mathbb{V}_{h,k}^{\rm div},\\
(\boldsymbol{\phi}_h, \nabla v_h)+\alpha(Q_hu_h, Q_hv_h)&=(f, Q_hv_h)\quad\forall~v_h\in V_h.
\end{aligned} 
\end{equation*} 
% \end{remark}

@@

% \subsection{Error analysis}
Applying the standard error analysis for VEMs, we have the following error estimate for the VEM \eqref{eq:cfmvem}.
\begin{theorem}\label{thm:cfmerrorestimateH1}
Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:cfmvem}. Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
\begin{equation}\label{eq:cfmerrorestimateH1}
|u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
\end{equation}
\end{theorem}
% \begin{proof}
% Take any $v_h\in V_h$. 
% Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
% \[
% \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
% \]
% \[
% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
% \]
% Combining the last two inequalities gives
% \[
% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
% \]
% By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
% \begin{align*}
% |v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
% % &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
% \end{align*}
% Hence we get from the triangle inequality and the last two inequalities that
% \begin{align*}  
% |u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
% &\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
% \end{align*}
% By the arbitrariness of $v_h\in V_h$, we derive
% \[
% |u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
% \]
% At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
% \end{proof}

@@

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}. We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Fig.~\ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
of nonconforming virtual element method \eqref{eq:vem} on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}
